A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-15 paper/ms.tex
update ms

		\subfloat{
			\includegraphics[width=0.49\textwidth]{f16.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit of Kepler 1627 Ab.}
    {\it Top:} 
    The time of each Kepler transit was measured, along with the local
    slope of the light curve.  The two quantities appear
    anti-correlated, which is most easily explained by starspot
    crossings during the first (second) half of transit inducing a
    positive (negative) TTV, provided that the orbit is prograde
    \citep{mazeh_time_2015}.  The units along the abscissa are most
    easily understood by considering that the stellar flux
    changes by $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
    {\it Bottom:} Radial velocities acquired using Keck/HIRES during
    the transit of 2021 Aug 7, observed simultaneously with MuSCAT3
    ({\it griz} photometry).  A quadratic baseline trend was allowed
    in the RV fit.  The best-fit sky-projected obliquity in this model
    is listed in red; the spectroscopic detection however has marginal statistical
    significance compared to a ``trend-only'' model.
    \label{fig:obliquity}
	}
\end{figure}
\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f14.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting
			exoplanets}.  Planets older than $10^9$ years are shown with gray
		markers.  Planets younger than a gigayear with ${\rm
			\tau}/\sigma_{\rm \tau} > 3$ are emphasized, for $\tau$ the age.
		\pn\ is shown with a
		star.  The large sizes of the youngest transiting planets could be
		explained by their primordial atmospheres not yet having
		evaporated; direct measurements of the atmospheric outflows or
		planetary masses would help to confirm this expectation.
		Selection effects may also be important.  Parameters are from the
		NASA Exoplanet Archive (2021 July 2).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

The authors are grateful to T{.}~David, J{.}~Winn, and A{.}~Howard for
illuminating discussions and guidance, and to R{.}~Kerr for kindly
providing us with the \citet{Kerr2021} membership list prior to its
publication.
The authors are also grateful to K{.}~Collins for
helping resolve the scheduling conflict that would have otherwise
prevented the MuSCAT3 observations.
% is grateful to G.~Zhou, B{.}~Tofflemire, A{.}~McWilliam,
% E{.}~Newton, M{.}~Kounkel, A{.}~Kraus, L{.}~Hillenbrand, and
% K{.}~Hawkins for the discussions on young stars, rotation, and lithium
% that encouraged this analysis.
%
L.G.B{.} acknowledges support from a Charlotte Elizabeth Procter
Fellowship from Princeton University, as well as from the TESS GI Program, programs
G011103 and G022117, through NASA grants 80NSSC19K0386 and
80NSSC19K1728.
%
%
Keck/NIRC2 imaging was acquired by programs 2015A/N301N2L
(PI: A.~Kraus) and 2019A/N069 (PI: E.~Petigura).
%
In addition, this paper is based in part on observations made with the
MuSCAT3 instrument, developed by the Astrobiology Center and under
financial supports by JSPS KAKENHI (JP18H05439) and JST PRESTO
(JPMJPR1775), at Faulkes Telescope North on Maui, HI, operated by the
Las Cumbres Observatory.
%
This work is partly supported by JSPS KAKENHI Grant Numbers 22000005,
JP15H02063, JP17H04574, JP18H05439, JP18H05442, JST PRESTO Grant
Number JPMJPR1775, the Astrobiology Center of National Institutes of
Natural Sciences (NINS) (Grant Number AB031010).
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
This paper also includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham,
S.~Seager, J.~Jenkins) and the many TESS team members for their
efforts to make the mission a continued success.
%
%
%This study was based in part on observations at Cerro Tololo
%Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
%2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
%Association of Universities for Research in Astronomy (AURA) under a
%cooperative agreement with the National Science Foundation.
%
%
Finally, this research has made use of the Keck Observatory Archive (KOA),
which is operated by the W. M. Keck Observatory and the NASA Exoplanet
Science Institute (NExScI), under contract with the National
Aeronautics and Space Administration.  We also thank the Keck
Observatory staff for their support of HIRES and remote observing.  We
recognize the importance that the summit of Maunakea has within the
indigenous Hawaiian community, and are deeply grateful to have the
opportunity to conduct observations from this mountain.
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%

>>>>

		\subfloat{
			\includegraphics[width=0.49\textwidth]{f16.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit of Kepler 1627 Ab.}
    {\it Top:} 
    The time of each Kepler transit was measured, along with the local
    slope of the light curve.  The two quantities appear
    anti-correlated, which is most easily explained by starspot
    crossings during the first (second) half of transit inducing a
    positive (negative) TTV, provided that the orbit is prograde
    \citep{mazeh_time_2015}.  The units along the abscissa are most
    easily understood by considering that the stellar flux
    changes by $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
    {\it Bottom:} Radial velocities acquired using Keck/HIRES during
    the transit of 2021 Aug 7, observed simultaneously with MuSCAT3
    ({\it griz} photometry).  A quadratic baseline trend was allowed
    in the RV fit.  The best-fit sky-projected obliquity in this model
    is listed in red; the spectroscopic detection however has marginal statistical
    significance compared to a ``trend-only'' model.
    \label{fig:obliquity}
	}
\end{figure}
\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f14.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting
			exoplanets}.  Planets older than $10^9$ years are shown with gray
		markers.  Planets younger than a gigayear with ${\rm
			\tau}/\sigma_{\rm \tau} > 3$ are emphasized, for $\tau$ the age.
		\pn\ is shown with a
		star.  The large sizes of the youngest transiting planets could be
		explained by their primordial atmospheres not yet having
		evaporated; direct measurements of the atmospheric outflows or
		planetary masses would help to confirm this expectation.
		Selection effects may also be important.  Parameters are from the
		NASA Exoplanet Archive (2021 Sept 15).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

The authors are grateful to T{.}~David, J{.}~Winn, and A{.}~Howard for
illuminating discussions and guidance, and to R{.}~Kerr for kindly
providing us with the \citet{Kerr2021} membership list prior to its
publication.
The authors are also grateful to K{.}~Collins for
helping resolve the scheduling conflict that would have otherwise
prevented the MuSCAT3 observations.
% is grateful to G.~Zhou, B{.}~Tofflemire, A{.}~McWilliam,
% E{.}~Newton, M{.}~Kounkel, A{.}~Kraus, L{.}~Hillenbrand, and
% K{.}~Hawkins for the discussions on young stars, rotation, and lithium
% that encouraged this analysis.
%
L.G.B{.} acknowledges support from a Charlotte Elizabeth Procter
Fellowship from Princeton University, as well as from the TESS GI Program, programs
G011103 and G022117, through NASA grants 80NSSC19K0386 and
80NSSC19K1728.
%
%
Keck/NIRC2 imaging was acquired by programs 2015A/N301N2L
(PI: A.~Kraus) and 2019A/N069 (PI: E.~Petigura).
%
In addition, this paper is based in part on observations made with the
MuSCAT3 instrument, developed by the Astrobiology Center and under
financial support by JSPS KAKENHI (JP18H05439) and JST PRESTO
(JPMJPR1775), at Faulkes Telescope North on Maui, HI, operated by the
Las Cumbres Observatory.
%
This work is partly supported by JSPS KAKENHI Grant Numbers 22000005,
JP15H02063, JP17H04574, JP18H05439, JP18H05442, JST PRESTO Grant
Number JPMJPR1775, the Astrobiology Center of National Institutes of
Natural Sciences (NINS) (Grant Number AB031010).
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
This paper also includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.
%
We thank the TESS Architects (G.~Ricker, R.~Vanderspek, D.~Latham,
S.~Seager, J.~Jenkins) and the many TESS team members for their
efforts to make the mission a continued success.
%
%
%This study was based in part on observations at Cerro Tololo
%Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
%2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
%Association of Universities for Research in Astronomy (AURA) under a
%cooperative agreement with the National Science Foundation.
%
%
Finally, this research has made use of the Keck Observatory Archive (KOA),
which is operated by the W. M. Keck Observatory and the NASA Exoplanet
Science Institute (NExScI), under contract with the National
Aeronautics and Space Administration.  We also thank the Keck
Observatory staff for their support of HIRES and remote observing.  We
recognize the importance that the summit of Maunakea has within the
indigenous Hawaiian community, and are deeply grateful to have the
opportunity to conduct observations from this mountain.
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%
